\documentclass[10pt, a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{changepage}
\usepackage[shortlabels]{enumitem}
\usepackage{microtype, xspace}
\usepackage{hyperref}

\newcommand{\vmargin}{2cm}
\newcommand{\hmargin}{2.5cm}
\geometry{top=\vmargin,
    bottom=\vmargin,
    left=\hmargin,
    right=\hmargin}
\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=cyan}

\pagenumbering{gobble}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlist{topsep=0pt, itemsep=0pt}

% BEGIN CUSTOM MACROS
% --------------------------------------------- %
\newcommand{\rangesep}{to\xspace}  % for date ranges
\renewcommand{\date}[1]{\textit{#1}}
\newcommand{\location}[1]{\textit{#1}}

\newcommand{\heading}[1]{
\makebox[0pt][l]{\Large \sc \hspace{2pt}#1}
\rule[-0.7ex]{\columnwidth}{0.5pt}\vspace{0.5ex}
}

\newcommand{\subheading}[1]{{\bfseries #1}}
\newcommand{\generalInfoSkip}{\vspace{0.3ex}}
\newcommand{\subheadSkip}{\vspace{0.7ex}}
\newcommand{\contentIndent}{\hspace{1em}}
% --------------------------------------------- %
% END CUSTOM MACROS


% BEGIN CUSTOM ENVIRONMENTS
% --------------------------------------------- %
\newenvironment{mysection}[1]
{\vspace{2.5ex}
\heading{#1}
\begin{adjustwidth}{0.3cm}{0cm}}
{\end{adjustwidth} }

\newenvironment{entry}
\par
{\vspace{0.1ex}}
{}
% --------------------------------------------- %
% END CUSTOM ENVIRONMENTS

\begin{document}

    \textbf{\LARGE Elijan J. Mastnak}

    \vspace{1.5ex}
    3 Evelyn Place \hfill Email: \href{mailto:ejmastnak@gmail.com}{\texttt{ejmastnak@gmail.com}}

    Princeton, NJ 05840 \hfill Webpage: \href{https://ejmastnak.github.io/}{\texttt{ejmastnak.github.io}}


    \begin{mysection}{General Information}

        \textbf{Citizenship:} United States and Slovenia (EU member state)

        \generalInfoSkip
        \textbf{Languages:} English, Slovene, Spanish

        \generalInfoSkip
        \textbf{Skills include:} clearly-communicated technical writing; teaching introductory through undergraduate physics, mathematics, and programming; {\LaTeX}, including real-time transcription of mathematical formulas; scientific Python (\texttt{NumPy}, \texttt{Matplotlib}, \texttt{SciPy}); vector graphics (\texttt{Tikz}; Inkscape); shell scripting and Unix utilities; Java; Git and GitHub; Vim/NeoVim.

    \end{mysection}

    \begin{mysection}{Education}
        \subheading{University of Ljubljana, Faculty of Math and Physics} \hfill \location{Ljubljana, Slovenia}

        \textit{Bachelor of Science in Physics} \hfill \date{October 2018 \rangesep September 2021}

        \vspace{0.1ex}
        \begin{entry}
            \hspace{1em} Thesis: ``End-to-End Classification for Discovery of New Processes in High-Energy Physics''

            \hspace{1em} Thesis webpage: \url{https://ejmastnak.github.io/seminar/seminar.html}
        \end{entry}
            
        \subheadSkip
        \subheading{Newport Harbor High School} \hfill \location{Newport Beach, CA}

        \textit{International Baccalaureate Diploma} \hfill \date{September 2014 \rangesep June 2017}

    \end{mysection}

    \begin{mysection}{Employment}
        \subheading{University of Ljubljana, Faculty of Math and Physics} \hfill \location{Ljubljana, Slovenia}

        \vspace{0.1ex}
        \textit{Private Contractor} \hfill \date{June 2021 \rangesep present}
        \begin{entry}
            Commissioned to typeset and translate the first-year physics curriculum to English, in textbook form, using recorded Slovene video lectures. Project goal: make the university's physics program more approachable to foreign-exchange students.    
        \end{entry}

        \subheadSkip
        \vspace{0.3ex}
        \subheading{TMG-BMC Ltd.} \hfill \location{Ljubljana, Slovenia}

        \textit{Data Analyst and Software Developer} \hfill \date{August 2019 \rangesep September 2021}

        \vspace{0.1ex}
        TMG-BMC is a biomechanics and kinesiology company specializing in high-end, non-invasive sensors for quantifying muscle function in professional athletes. Webpage: \url{https://www.tmg-bodyevolution.com/}

        \begin{itemize}
        
            \item Analysis of 1D biomechanical time-series data from TMG, EMG, load cell, and MC sensors: detecting and quantifying twitch potentiation; quantifying contraction time, maximum muscle displacement, and rate of force development.

            Techniques include: numerical integration and differentiation, Lagrange interpolation, curve fitting, iterative methods for nonlinear equations, peak detection, filtering, statistical parametric mapping.

            \item Developed cross-platform user interface (in Java using Swing) to make above-described analysis accessible to non-technical users.

            \item Regularly worked with professional (including Olympic) athletes, mostly in track and field.
        
        \end{itemize}

        \subheadSkip
        \subheading{Newport Harbor High School} \hfill \location{Newport Beach, CA}

        Two positions: \textit{Academic Tutor} and \textit{Soccer Coach} \hfill \date{August 2017 \rangesep June 2018}

        \begin{itemize}
        
            \item Tutor in physics, math and programming for Newport Harbor High School's AVID program, which provides school-sponsored after-school tutoring to students.

            \item Assistant coach in the boy's soccer program for the academic year (as an alumnus and former varsity captain); head coach of the Frosh-Soph team in the 2017-18 winter season.
        
        \end{itemize}

        \subheadSkip
        \subheading{Self-Employed} \hfill \location{Newport Beach, CA}

        \vspace{0.1ex}
        \textit{Private Tutor} \hfill \date{September 2017 \rangesep June 2018}
        \begin{entry}
            Worked as a private tutor in math and physics in the Newport Beach and Costa Mesa area; served students from Newport Harbor and Corona del Mar High School.
        \end{entry}

    \end{mysection}

\end{document}
