\documentclass[10pt, a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{changepage}
\usepackage[shortlabels]{enumitem}
\usepackage{microtype, xspace}
\usepackage{hyperref}

\newcommand{\hmargin}{2.5cm}
\geometry{top=2.0cm,
    bottom=2.0cm,
    left=\hmargin,
    right=\hmargin}
\hypersetup{colorlinks=true, linkcolor=cyan, urlcolor=cyan}

\pagenumbering{gobble}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlist{topsep=0pt, itemsep=0pt}

% Footer configuration
%--------------------------------------------%
\usepackage{fancyhdr, extramarks}
\pagestyle{fancy}

\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\small \textit{Source code available at \textup{\href{https://github.com/ejmastnak/cv}{\texttt{github.com/ejmastnak/cv}}} under the \textup{CC BY-NC-SA 4.0} license.}}

% \renewcommand{\sectionmark}[1]{
%     \markboth{\thesection. \ #1}
%     {\noexpand\firstsubsectiontitle}
%     \global\firstsubsectionmarktrue}
% \renewcommand{\subsectionmark}[1]{
%     \markright{\thesubsection. \, #1}
%     \iffirstsubsectionmark
% \edef\firstsubsectiontitle{\thesubsection. \, #1}
% \fi
% \global\firstsubsectionmarkfalse}
% \newif\iffirstsubsectionmark
% \def\firstsubsectiontitle{}

\setlength{\headheight}{14pt} 
%--------------------------------------------%
% End footer configuration

% BEGIN CUSTOM MACROS
% --------------------------------------------- %
\newcommand{\rangesep}{to\xspace}  % for date ranges
\renewcommand{\date}[1]{\textit{#1}}
\newcommand{\location}[1]{\textit{#1}}
\newcommand{\contentType}[1]{\textit{#1}}

\newcommand{\heading}[1]{
\makebox[0pt][l]{\Large \sc \hspace{2pt}#1}
\rule[-0.7ex]{\columnwidth}{0.5pt}\vspace{1.0ex}
}

\newcommand{\subheading}[1]{{\bfseries #1}}
\newcommand{\generalInfoSkip}{\vspace{0.8ex}}
\newcommand{\subheadSkip}{\vspace{1ex}}
\newcommand{\contentIndent}{\hspace{1em}}
% --------------------------------------------- %
% END CUSTOM MACROS


% BEGIN CUSTOM ENVIRONMENTS
% --------------------------------------------- %
\newenvironment{mysection}[1]
{\vspace{2.5ex}
\heading{#1}
\begin{adjustwidth}{0.3cm}{0cm}}
{\end{adjustwidth} }

\newenvironment{entry}
\par
{\vspace{0.1ex}}
{}
% --------------------------------------------- %
% END CUSTOM ENVIRONMENTS

\begin{document}

    \textbf{\LARGE Elijan J. Mastnak}

    \vspace{1.5ex}
    Webpage: \href{https://ejmastnak.com/}{\texttt{www.ejmastnak.com}}\\
    GitHub: \href{https://github.com/ejmastnak}{\texttt{www.github.com/ejmastnak}}\\
    Email: \href{mailto:ejmastnak@gmail.com}{\texttt{ejmastnak@gmail.com}}

    \begin{mysection}{General Information}
        \textbf{Citizenship:} United States and Slovenia (an EU member state)

        \generalInfoSkip
        \textbf{Fluent languages:} English, Slovene, Spanish

        \generalInfoSkip
        \textbf{Skills include:} clearly-communicated, human-friendly technical writing;
        teaching introductory through undergraduate physics, mathematics, signal processing, and computer programming;
        the scientific Python stack (NumPy, Matplotlib, SciPy);
        {\LaTeX} and digital typesetting;
        vector graphics (Tikz; Inkscape);
        Bash scripting and the Unix core utilities;
        \texttt{systemd}-based Linux systems;
        creation and maintenance of static websites.
    \end{mysection} 

    \begin{mysection}{Portfolio}
        \subheading{Real-time LaTeX Using (Neo)Vim} \hfill \contentType{Tutorial series/technical writing}
        \begin{entry}
            \hspace{1em} \textls[-5]{A 7-article guide to supercharged mathematical typesetting} \href{https://github.com/lervag/vimtex/#vimtex-on-the-web}{officially endorsed} \textls[-5]{by the VimTeX project}.

            \hspace{1em} See it here:
            \href{https://www.ejmastnak.com/tutorials/vim-latex/intro/}{\url{www.ejmastnak.com/tutorials/vim-latex/intro/}}
        \end{entry}
            
        \subheadSkip
        \subheading{Solved exercises and lecture notes} \hfill \contentType{Educational writing}
        \begin{entry}
            \hspace{1em} 1500+ pages of solved exercises and lecture notes in undergraduate physics, typeset in LaTeX.

            \hspace{1em} See it here:
            \href{https://www.ejmastnak.com/notes/fmf/fmf/}{\url{www.ejmastnak.com/notes/fmf/fmf/}}
        \end{entry}

        \subheadSkip
        \subheading{Arch Linux Post-Installation Tutorials} \hfill \contentType{Technical writing}
        \begin{entry}
            \hspace{1em} \textls[-15]{Bite-sized, actionable tutorials for a functional work environment after a minimal install of Arch Linux.}

            \hspace{1em} See it here:
            \href{https://www.ejmastnak.com/tutorials/arch/about/}{\url{www.ejmastnak.com/tutorials/arch/about/}}

        \end{entry}

    \end{mysection}

    \begin{mysection}{Education}
        \subheading{University of Ljubljana, Faculty of Math and Physics} \hfill \location{Ljubljana, Slovenia}

        \textit{Bachelor of Science in Physics} \hfill \date{October 2018 \rangesep September 2021}

        \vspace{0.1ex}
        \begin{entry}
            \hspace{1em} Undergraduate ``mini-thesis'': ``End-to-End Particle Classification in High-Energy Physics''

            \hspace{1em} Thesis webpage:
            \href{https://www.ejmastnak.com/projects/seminar/}{\url{www.ejmastnak.com/projects/seminar/}}

        \end{entry}
            
        \subheadSkip
        \subheading{Newport Harbor High School} \hfill \location{Newport Beach, CA}

        \textit{International Baccalaureate Diploma} \hfill \date{September 2014 \rangesep June 2017}
    \end{mysection}

    \begin{mysection}{Employment}
        \subheading{TMG-BMC Ltd.} \hfill \location{Ljubljana, Slovenia}

        \textit{Programmatic Analysis of Time-Series Biomechanics Data} \hfill \date{August 2019 \rangesep present}

        \vspace{0.1ex}
        TMG-BMC is a biomechanics and kinesiology company specializing in high-end, non-invasive sensors for quantifying muscle function in professional athletes. Webpage: \url{https://www.tmg-bodyevolution.com/}

        \begin{itemize}
        
            \item Analysis of 1D biomechanical time-series data from TMG, EMG, load cell, and MC sensors: detecting and quantifying twitch potentiation; quantifying contraction time, maximum muscle displacement, and rate of force development.

            Techniques include numerical integration and differentiation, Lagrange interpolation, curve fitting, iterative methods for nonlinear equations, peak detection, filtering, statistical hypothesis testing, statistical parametric mapping.

            \item Developed cross-platform user interface (in Java using Swing) to make above-described analysis accessible to non-technical users.

            \item Trained to use TMG, EMG, load cell, and MC sensors.

            \item Regularly worked with professional (including Olympic) athletes, mostly in track and field.
        
        \end{itemize}

        \subheadSkip
        \subheading{University of Ljubljana, Faculty of Math and Physics} \hfill \location{Ljubljana, Slovenia}

        \vspace{0.1ex}
        \textit{Textbook Author} \hfill \date{June 2021 \rangesep December 2021}
        \begin{entry}
            Commissioned to transform the Faculty's introductory mechanics course into English-language textbook form, using recorded Slovene video lectures. Project goal: make the university's physics program more approachable to foreign-exchange students.
        \end{entry}

    \end{mysection}

    \newpage
    \begin{mysection}{Employment \large{(continued)}}

        \subheadSkip
        \subheading{Newport Harbor High School} \hfill \location{Newport Beach, CA}

        Two positions: \textit{Academic Tutor} and \textit{Soccer Coach} \hfill \date{August 2017 \rangesep June 2018}

        \begin{itemize}
        
            \item Tutor in physics, math and programming for Newport Harbor High School's AVID program, which provides school-sponsored after-school tutoring to students.

            \item Assistant coach in the boy's soccer program for the academic year (as an alumnus and former varsity captain); head coach of the Frosh-Soph team in the 2017-18 winter season.
        
        \end{itemize}

        \subheadSkip
        \subheading{Self-Employed} \hfill \location{Newport Beach, CA}

        \vspace{0.1ex}
        \textit{Private Tutor in Math and Physics} \hfill \date{September 2017 \rangesep June 2018}
        \begin{entry}
            Worked as a private tutor in math and physics in the Newport Beach and Costa Mesa area; served students from Newport Harbor and Corona del Mar High School.
        \end{entry}
    \end{mysection} 

\end{document}
